---
title: "Alcohol vs Seat choice"
author: "Elizabeth Rivera"
date: "Fall 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

##  methods  
Seat is a categorical variable.

Alcohol is a numerical variable. 

For this problem we explain alcohol consumption based on where people sit.

Therefore the helper file is the numerical categorical file. 

$H_0$: The null hypothesis is there is no difference in alcohol consumption based on where you sit.  

$H_A$: The alternative hypothesis is that there is a difference in alcohol consumption based on where you sit.   


```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```



## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


Based on the box plot, people that sit in the back consume more alcohol than people who sit in the front or in the middle. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
Based on the numerical summary evidence shows that on average people who sit in the back consume 8.5 drinks a week. On average people who sit in the front and in the middle consume 1-3 drinks a week.  

## Inferential Tests

## Conclusions


